### 2018-12-12 main-plos.tex
misc

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
% Please use "sentence case" for title and headings (capitalize only the first
% word in a title (or heading), the first word in a subtitle (or subheading),
% and any proper nouns).
% % \title{Machine learning of prostate MRI: towards improved non-invasive
% % prostate cancer characterization}
\textbf\newline{Machine learning of prostate MRI: towards improved non-invasive
prostate cancer characterization}
}
\newline
% Insert author names, affiliations and corresponding author email (do not
% include titles, positions, or degrees).
% % \author[dia,inf]{Jussi~Toivonen\corref{cor1}}
% % \author[dia,inf]{Ileana~Montoya~Perez}
% % \author[dia,inf]{Parisa~Movahedi}
% % \author[dia,inf,pet]{Harri~Merisaari}
% % \author[dia]{Marko~Pesola}
% % \author[pat]{Pekka~Taimen}
% % \author[uro]{Peter~J.~Boström}
% % \author[inf]{Jonne~Pohjankukka}
% % \author[dia,med]{Aida~Kiviniemi}
% % \author[inf]{Tapio~Pahikkala}
% % \author[dia,med]{Hannu~J.~Aronen}
% % \author[dia,rad]{Ivan~Jambor}
\\
%Jussi Toivonen\textsuperscript{1,2*\textcurrency},
Jussi~Toivonen\textsuperscript{1,2*},
Ileana~Montoya~Perez\textsuperscript{1,2},
Parisa~Movahedi\textsuperscript{1,2},
Harri~Merisaari\textsuperscript{1,2,3},
Marko~Pesola\textsuperscript{1},
Pekka~Taimen\textsuperscript{4},
Peter~J.~Boström\textsuperscript{5},
Jonne~Pohjankukka\textsuperscript{2},
Aida~Kiviniemi\textsuperscript{1,6},
Tapio~Pahikkala\textsuperscript{2},
Hannu~J.~Aronen\textsuperscript{1,6},
Ivan~Jambor\textsuperscript{1,7}
\\
\bigskip
\newcommand{\turku}{Turku, Finland}
\newcommand{\utu}{University of Turku}
\newcommand{\tyks}{Turku University Hospital}
\newcommand{\deptdr}{Dept.\ of Diagnostic Radiology}
\newcommand{\deptft}{Dept.\ of Future Technologies}
% % \address[dia]{Department of Diagnostic Radiology, \utu}
% % \address[inf]{Department of Information Technology, \utu}
% % \address[pet]{Turku PET Centre, \utu}
% % \address[pat]{Department of Pathology, University of Turku and \tyks}
% % \address[uro]{Department of Urology, \tyks}
% % \address[med]{Medical Imaging Centre of Southwest Finland, \tyks}
% % \address[rad]{Department of Radiology, University of Massachusetts---Baystate, Springfield, MA, USA}
%\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\textbf{1} \deptdr, \utu, \turku\\
\textbf{2} \deptft, \utu, \turku\\
\textbf{3} Turku PET Centre, \utu, \turku\\
\textbf{4} Dept. of Pathology, \utu{} and \tyks, \turku\\
\textbf{5} Dept. of Urology, \tyks, \turku\\
\textbf{6} Medical Imaging Centre of Southwest Finland, \tyks, \turku\\
\textbf{7} Dept. of Radiology, University of Massachusetts---Baystate, Springfield, MA, USA\\
\bigskip

>>>>

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}
\newcommand{\turku}{Turku, Finland}
\newcommand{\utu}{University of Turku}
\newcommand{\tyks}{Turku University Hospital}
\newcommand{\deptdr}{Dept.\ of Diagnostic Radiology}
\newcommand{\deptft}{Dept.\ of Future Technologies}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
% Please use "sentence case" for title and headings (capitalize only the first
% word in a title (or heading), the first word in a subtitle (or subheading),
% and any proper nouns).
% % \title{Machine learning of prostate MRI: towards improved non-invasive
% % prostate cancer characterization}
\textbf\newline{Machine learning of prostate MRI:\ towards improved non-invasive
prostate cancer characterization}
}
\newline
% Insert author names, affiliations and corresponding author email (do not
% include titles, positions, or degrees).
% % \author[dia,inf]{Jussi~Toivonen\corref{cor1}}
% % \author[dia,inf]{Ileana~Montoya~Perez}
% % \author[dia,inf]{Parisa~Movahedi}
% % \author[dia,inf,pet]{Harri~Merisaari}
% % \author[dia]{Marko~Pesola}
% % \author[pat]{Pekka~Taimen}
% % \author[uro]{Peter~J.~Boström}
% % \author[inf]{Jonne~Pohjankukka}
% % \author[dia,med]{Aida~Kiviniemi}
% % \author[inf]{Tapio~Pahikkala}
% % \author[dia,med]{Hannu~J.~Aronen}
% % \author[dia,rad]{Ivan~Jambor}
\\
%Jussi Toivonen\textsuperscript{1,2*\textcurrency},
Jussi~Toivonen\textsuperscript{1,2*},
Ileana~Montoya~Perez\textsuperscript{1,2},
Parisa~Movahedi\textsuperscript{1,2},
Harri~Merisaari\textsuperscript{1,2,3},
Marko~Pesola\textsuperscript{1},
Pekka~Taimen\textsuperscript{4},
Peter~J.~Boström\textsuperscript{5},
Jonne~Pohjankukka\textsuperscript{2},
Aida~Kiviniemi\textsuperscript{1,6},
Tapio~Pahikkala\textsuperscript{2},
Hannu~J.~Aronen\textsuperscript{1,6},
Ivan~Jambor\textsuperscript{1,7}
\\
\bigskip
% % \address[dia]{Department of Diagnostic Radiology, \utu}
% % \address[inf]{Department of Information Technology, \utu}
% % \address[pet]{Turku PET Centre, \utu}
% % \address[pat]{Department of Pathology, University of Turku and \tyks}
% % \address[uro]{Department of Urology, \tyks}
% % \address[med]{Medical Imaging Centre of Southwest Finland, \tyks}
% % \address[rad]{Department of Radiology, University of Massachusetts---Baystate, Springfield, MA, USA}
%\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\textbf{1} \deptdr, \utu, \turku\\
\textbf{2} \deptft, \utu, \turku\\
\textbf{3} Turku PET Centre, \utu, \turku\\
\textbf{4} Dept.\ of Pathology, \utu{} and \tyks, \turku\\
\textbf{5} Dept.\ of Urology, \tyks, \turku\\
\textbf{6} Medical Imaging Centre of Southwest Finland, \tyks, \turku\\
\textbf{7} Dept.\ of Radiology, University of Massachusetts---Baystate,
Springfield, MA, USA\\
\bigskip
